EuPPollNet: A European database of plant-pollinator networks

### 2024-05-16 Manuscript/EuPPollNet_Ms.qmd
second paragraph

#Check number of studies by habitat
studies_by_habitat = data %>% 
select(Study_id, EuPPollNet_habitat) %>% 
distinct() %>%  
group_by(EuPPollNet_habitat) %>% 
summarise(Habitat_count = n()) %>% 
slice_max(Habitat_count, n = 3) %>% 
mutate(EuPPollNet_habitat = tolower(EuPPollNet_habitat))
#Check number of sampling sites by habitat
networks_by_habitat = data %>% 
select(Network_id, EuPPollNet_habitat) %>% 
distinct() %>%  
group_by(EuPPollNet_habitat) %>% 
summarise(Habitat_count = n()) %>% 
slice_max(Habitat_count, n = 3) %>% 
mutate(EuPPollNet_habitat = tolower(EuPPollNet_habitat))
#Check number of studies by bioregion
studies_by_bioregion = data %>% 
select(Study_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) %>% 
slice_max(Bioregion_count, n = 3) %>% 
mutate(Bioregion = tolower(Bioregion))
#Check number of sampling sites by bioregion
networks_by_bioregion = data %>% 
select(Network_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) %>% 
slice_max(Bioregion_count, n = 3) %>% 
mutate(Bioregion = tolower(Bioregion))

@@

Bees conducted the majority of the interactions at the metaweb level, but their relative relevance changed across habitats and bioclimatic regions. For instance, plant-pollinator communities in the Mediterranean were dominated by bees, while communities in Alpine or Boreal regions were especially fly species rich or fly-dominated. These patterns are consistent with our current understanding of bee diversity, which peaks in dry or temperate areas [@orr2021; @leclercq2023]; and with the fact that colder environments (i.e., altitude and latitude wise) harbor a larger fraction of fly pollinators compared to other taxa [@elberling1999; @lefebvre2018]. In addition, beetles were only species rich in the Mediterranean region. Although the networks from the database are visitation networks and do not capture pollinator efficiency [@ballantyne2015], the high proportion of beetles as floral visitors in the Mediterranean provides further support for their role as pollinators in this region [@herrera2019; @leon2022]. The number of butterfly species and interactions were relatively low compared to the other taxa. Although Europe contains a little number of butterfly species compared to other areas of the world [@ollerton2017], their relevance as pollinators is likely under-estimated within this database as sampling methodologies for other insects pollinators (e.g., bees or flies) generally require less sampling distance and cover less space. Honey bees did one third of the total recorded interactions per network, highlighting their high abundances in natural communities and possibly impacting negatively wild pollinators.

-Presence of honey bees in context with previous studies
Maybe cite Proc B and myself?

@@

>>>>

#Check number of studies by habitat
studies_by_habitat = data %>% 
select(Study_id, EuPPollNet_habitat) %>% 
distinct() %>%  
group_by(EuPPollNet_habitat) %>% 
summarise(Habitat_count = n()) %>% 
slice_max(Habitat_count, n = 3) %>% 
mutate(EuPPollNet_habitat = tolower(EuPPollNet_habitat))
#Check number of sampling sites by habitat
networks_by_habitat = data %>% 
select(Network_id, EuPPollNet_habitat) %>% 
distinct() %>%  
group_by(EuPPollNet_habitat) %>% 
summarise(Habitat_count = n()) %>% 
slice_max(Habitat_count, n = 3) %>% 
mutate(EuPPollNet_habitat = tolower(EuPPollNet_habitat))
#Check number of studies by bioregion
studies_by_bioregion = data %>% 
select(Study_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) %>% 
slice_max(Bioregion_count, n = 3) %>% 
mutate(Bioregion = tolower(Bioregion))
#Check number of sampling sites by bioregion
networks_by_bioregion = data %>% 
select(Network_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) %>% 
slice_max(Bioregion_count, n = 3) %>% 
mutate(Bioregion = tolower(Bioregion))
#Check percentage of Apis mellifera across networks
apis_percent_networks = data %>% 
filter(Pollinator_accepted_name == "Apis mellifera") %>%
group_by(Study_id) %>% 
mutate(Apis = "Yes") %>% 
distinct(Study_id, Apis) %>% 
nrow() / nlevels(factor(data$Study_id)) *100

@@

Bees conducted the majority of the interactions at the metaweb level, but their relative relevance changed across habitats and bioclimatic regions. For instance, plant-pollinator communities in the Mediterranean were dominated by bees, while communities in Alpine or Boreal regions were especially fly species rich or fly-dominated. These patterns are consistent with our current understanding of bee diversity, which peaks in dry or temperate areas [@orr2021; @leclercq2023]; and with the fact that colder environments (i.e., altitude and latitude wise) harbor a larger fraction of fly pollinators compared to other taxa [@elberling1999; @lefebvre2018]. In addition, beetles were only species rich in the Mediterranean region. Although the networks from the database are visitation networks and do not capture pollinator efficiency [@ballantyne2015], the high proportion of beetles as floral visitors in the Mediterranean provides further support for their role as pollinators in this region [@herrera2019; @leon2022]. The number of butterfly species and interactions were relatively low compared to the other taxa. While Europe contains fewer butterfly species than other regions of the world [@ollerton2017], their relevance as pollinators is likely underestimated within this database. This is because a large fraction (~40%) of studies did not sample butterflies, and conventional sampling methods for monitoring other insect pollinators (e.g., bees or flies) may be inadequate for sampling plant-butterfly interactions [@isaac2011]. Honey bees were present in `r round(apis_percent_networks, 1)`% of networks and conducted in average a third of the total interactions per network. This proportion is higher that the one found when considering only natural communities at a global scale [~13%\; @hung2018], which highlights the need of further work evaluating how honey bees and their management impact natural pollinator communities.

@@

Connectance
Nestedness
Pattern across latitude
